Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-10 prop_letter.tex
After meeting...

\begin{abstract}
It is well-known that any quantum measurement can be only performed
in finite precision. However, quantum theory is usually based on infinitely
precise real and complex numbers, and physicists handle this imperfection
by statistical methods without understanding how finite precision
measurement affect the mathematical foundation of quantum theory.
Our purpose here is to examine a quantum model cooperating the idea
of finite precision at very beginning. Within our quantum interval-valued
probability measure (QIVPM) framework, we found a QIVPM become classical
when the projectors all commute, and the expectation value of an observable
can still be computed as expected. Two fundamental quantum theorems,
the Kochen-Specker and Gleason theorem, can be reformulated by QIVPM
given a particular choice of intervals, and we can discuss their validity
within a certain bound. Our research provides a new insight to quantify
the idea of finite precision measurement, and provides a possible
resolution of the Meyer-Mermin debate on the impact of finite precision
on the Kochen-Specker theorem.
\end{abstract}

@@

Here we develop a mathematical framework that includes the uncertainties of finite precision and imperfections in the quantum measurement process.  Our first observation is that essential objectives of our program to
achieve a computable theory of quantum mechanics and finite-resource
measurement, attempted previously with computable number
systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical interval-valued probability
measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework, which will provide a quantitative description of the impact of finite precision on the foundations of quantum mechanics.

@@

In particular, the effect of finite precision on contextuality, and the
Kochen-Specker theorem, is shown to have a resolution in terms of the quantum interval-valued probability measure framework that we introduce.  To proceed, we use a formulation of the Mermin square that uses the
expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude that
they correspond to the limit of an infinite number of precise
intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
respectively.

\begin{itemize}
\item Develop a framework that includes the uncertainties of finite precision in the quantum measurement process.
\item Provide a quantitative description of the impact of finite precision on the foundations of quantum mechanics.
\item In particular, the effect of finite precision on contextuality is shown to have a resolution in terms of the quantum interval valued probability measure framework that we introduce.
\item A key aspect of quantum measurement is its stochastic nature as reflected in Born's rule.  Gleason's theorem establishes the existence of a unique state (in Hilbert spaces of dimension $\ge 3$), the probabilities of whose outcomes are computed from Born's rule assuming infinite precision.  Then it is legitimate to question what happens when infinite precision cannot be achieved.
\item 
\end{itemize}

Our first observation is that essential objectives of our program to
achieve a computable theory of quantum mechanics and finite-resource
measurement, attempted previously with computable number
systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical interval-valued probability
measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by axiomatizing a quantum interval-valued probability measure (QIVPM)
framework exploiting the fact that a density matrix approach can be
considered as equivalent to a description of quantum states using
probability measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
One result is that the expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude that
they correspond to the limit of an infinite number of precise
intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
respectively.

>>>>

\begin{abstract}

We present a mathematical framework based on quantum interval-valued
probability measures to study the effect of experimental imperfections
and finite precision measurements on defining features of quantum
mechanics such as contextuality and the Born rule. While foundational
results such as the Kochen-Specker and Gleason theorems fail to hold
in general in a world with limited resources, when we allow infinite
precision, their validity is recovered.  However, we are able to use
the interval-valued framework to establish bounds on the validity of
those theorems in realistic experimental environments. In this way,
not only can we quantify the idea of finite-precision measurement
within our theory, but we can also suggest a possible resolution of
the Meyer-Mermin debate on the impact of finite-precision measurement
on the Kochen-Specker theorem.

\end{abstract}

@@

Here we develop a mathematical framework that includes the uncertainties of finite precision and imperfections in the quantum measurement process.  Our first observation is that essential objectives of our program to
achieve a computable theory of quantum mechanics and finite-resource
measurement, attempted previously with computable number
systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical interval-valued probability
measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework, which will provide a quantitative description of the impact of finite precision quantum measurements.

@@

In particular, the effect of finite precision on contextuality and the
Kochen-Specker theorem is shown to have a resolution in terms of our quantum interval-valued probability measure framework.  To proceed, we use a formulation of the Mermin square that uses the
expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude that
they correspond to the limit of an infinite number of precise
intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
respectively.

${\bullet}$ A key aspect of quantum measurement is its stochastic nature as reflected in Born's rule.  Gleason's theorem establishes the existence of a unique state (in Hilbert spaces of dimension $\ge 3$), the probabilities of whose outcomes are computed from Born's rule assuming infinite precision.  Then it is legitimate to question what happens when infinite precision cannot be achieved.

${\bullet}$ Exploiting the fact that a density matrix approach can be
considered as equivalent to a description of quantum states using
probability measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
